Exploring the Design Space of Differentially Private Bayesian Inference under Hellinger Distance

### 2019-01-18 ICML2019/main.tex
move proof about accuracy into Appendix

\subsubsection{Accuracy Bound for Laplace Mechanism}
\label{subsec_accuracy_lap}
Given $Y \thicksim \lap{0}{b}$, we have\cite{dwork2014algorithmic}:$\Pr[|Y| \geq t \cdot b] = e^{- t}.$\\
Based on this, we get:$\Pr[|Y| \geq t] = e^{- \frac{t \epsilon}{\Delta \bysinfer}}$, where $Y \thicksim \lap{0}{\frac{\Delta \bysinfer}{\epsilon}}$ in our setting.

@@

>>>>

\subsubsection{Accuracy Bound for Laplace Mechanism}
\label{subsec_accuracy_lap}
\begin{lem}
\label{lem_acc_lap}
Given $Y \thicksim \lap{0}{b}$, the accuracy bound developed for $\lapmech$ is:
\begin{align*}
&
\Pr\left[
\begin{aligned}
\lefteqn{\hellinger(\bysinfer(\dataobs), r_L )}\\ 
&= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)
\end{aligned}
\right]
\\
&\qquad = 
\begin{cases}
\frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}}) &  t \geq 0\\
\frac{1}{2} (e^{\frac{\epsilon (t + 1)}{\Delta \bysinfer}} - e^{\frac{\epsilon (t)}{\Delta \bysinfer}}) & t < 0
\end{cases}
\end{align*}
where $\betad(\alpha, \beta)$ is the true posterior distribution, i.e., $\bysinfer(\dataobs) = \betad(\alpha, \beta)$, and $r_L$ be the posterior produced by Laplace mechanism, i.e., $r_L = \betad(\alpha + \lfloor Y \rfloor, \beta - \lfloor Y \rfloor)$.
\end{lem}
(Proof is in Appendix III)

@@

\end{proof}

\section*{Appendix III}
\begin{proof} of Lemma \ref{lem_acc_lap}.

Given $Y \thicksim \lap{0}{b}$, we have\cite{dwork2014algorithmic}:$\Pr[|Y| \geq t \cdot b] = e^{- t}.$\\
Based on this, we get:$\Pr[|Y| \geq t] = e^{- \frac{t \epsilon}{\Delta \bysinfer}}$, where $Y \thicksim \lap{0}{\frac{\Delta \bysinfer}{\epsilon}}$ in our setting.
